---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# data.iquizoo

<!-- badges: start -->
[![R-CMD-check](https://github.com/iquizoo/data.iquizoo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/iquizoo/data.iquizoo/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/iquizoo/data.iquizoo/graph/badge.svg)](https://app.codecov.io/gh/iquizoo/data.iquizoo)
<!-- badges: end -->

The goal of data.iquizoo is to provide datasets for IQUIZOO workflows.

## Installation

You can install the development version of data.iquizoo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("iquizoo/data.iquizoo")
```

Or you can install from [r-universe](https://iquizoo.r-universe.dev/) with:

``` r
install.packages("data.iquizoo", repos = c(getOption("repos"), "https://iquizoo.r-universe.dev"))
```

## Example

The main parts of the package is a dataset: `game_info` containing basic information about games. Here is a simple example:

```{r example}
library(data.iquizoo)
# for long-int identifiers
requireNamespace("bit64", quietly = TRUE)
# show the first few rows of the data
head(game_info)
```

Some functions are also provided to help you work with the datasets. For example:

```{r example2}
library(data.iquizoo)
# some other useful functions
game_id <- bit64::as.integer64(305067065282821)
match_info(game_id, to = "game_name")
merge_preproc(data.frame(game_id = game_id))
```

## Contributing

We develop with the [github flow](https://docs.github.com/en/get-started/quickstart/github-flow) for its simplicity of this package.
