---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# data.iquizoo

<!-- badges: start -->
[![R-CMD-check](https://github.com/psychelzh/data.iquizoo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/psychelzh/data.iquizoo/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of data.iquizoo is to provide datasets for IQUIZOO workflows. It originally lived in dataproc.iquizoo package, and then we divided it into two new packages: data.iquizoo and preproc.iquizoo (see [psychelzh/dataproc.iquizoo#42](https://github.com/psychelzh/dataproc.iquizoo/issues/42) for more discussions on this decision).

## Installation

You can install the development version of data.iquizoo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("psychelzh/data.iquizoo")
```

## Example

This package only stores data, so there is no function to call. You can load the package and see the data:

```{r example}
# for long-int identifiers
requireNamespace("bit64", quietly = TRUE)
data(game_info, game_indices, package = "data.iquizoo")
# basic example code
head(game_info)
head(game_indices)
```

## Contributing

We develop with the [github flow](https://docs.github.com/en/get-started/quickstart/github-flow) for its simplicity of this package.
